Sampling requirements to detect ecosystem change

### 2019-11-21 R/temporal-sampling.Rmd
comment the weird creation of a fake data table (keeping it for later)

```{r read zurich data, include=T}
zh <- read.delim(paste0(getpath4data(),"ZH17_21_clado.txt")); is.zh=T
zh2 <- read.delim(paste0(getpath4data(),"VAR10-10-clado.txt")); is.zh=F
zh3 <- cbind(zh, matrix(rep(0,nrow(zh)*(ncol(zh)-1)), nrow(zh)))
zh3 <- rbind(zh3, cbind(matrix(c(1700:1710), rep(0,10*(ncol(zh)-1))),unlist(as.vector(zh2[1:10,-1]))) )
zh<-zh3
```

>>>>

```{r read zurich data, include=T}
zh <- read.delim(paste0(getpath4data(),"ZH17_21_clado.txt")); is.zh=T
# zh2 <- read.delim(paste0(getpath4data(),"VAR10-10-clado.txt")); is.zh=F
# zh3 <- cbind(zh, matrix(rep(0,nrow(zh)*(ncol(zh)-1)), nrow(zh)))
# zh3 <- rbind(zh3, cbind(matrix(c(1700:1710), rep(0,10*(ncol(zh)-1))),unlist(as.vector(zh2[1:10,-1]))) )
# zh<-zh3
```
